### 2023-04-23 main.tex
kk

At each site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ denotes the number of particles of species $a\in \{1,\ldots,N\}$ at site $x\in V$. On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$. Then, the configuration space of the process on the graph $G$ is 

@@

\Omega_{x}:=\left\{(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{a=1}^{N}n_{a}^{x}=\twoj\right\}

@@

where the quantities $ \omega_{x,y}\geq 0$ are called conductances and $\Gamma_{x}\geq 0$ local inhomogeneities. The generator $\mathcal{L}_{x,y}$ is called the \textit{edge generator}, while $\mathcal{L}_{x}$ is called the \textit{site generator}. These linear operators act on functions $f:\Omega\to \mathbb{R}$ as follows

@@

This means that on the edge $(x,y)\in \mathcal{E}$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$ a particle of type $a$ at site $x$ is exchanged with a particle of type $b$ at site $y$; furthermore, on each site $x\in V$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$ a particle of type $b$ is replaced with a particle of type $a$. For the sake of notation we denote $|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}$. 
See Figure \ref{fig:1}, Figure \ref{fig:2}for a visual description of the dyamics. 

@@

\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V

@@

\subsection{The Lie algebraic description}

Consider the Lie algebra $gl(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{cb}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$ and $\sum_{i=1}^N \lambda_i = \nu$. We assume $\lambda_i\geq \lambda_{i+1}$ without loss of generality.
We are interested in the {\em symmetric} finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}
\end{equation} 
The dimension $M$ of this symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
\begin{equation}
	M= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space $\mathbb{C}^{M}$ are the column vectors 
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu
\end{equation}
%where $\sum_{a=1}^{N}n_{i}=\nu$. 
This basis vector satisfy the orthogonality relation with respect to the Euclidean scalar product 
\begin{equation}\label{ortho}
   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a},n_{a}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronhecker delta. 
The explicit actions of the algebra generators on the vectors $|n\rangle$ are the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle\quad a=b
	\end{cases}
\end{equation}  
One can check that the matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
\newline 
\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
\\ \\
\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements

@@

>>>>

At each vertex site $x\in V$, we describe the occupation with an $N-$dimensional vector $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$ in which the value of the $a$-th component $n_{a}^{x}$ denotes the number of particles of species $a\in \{1,\ldots,N\}$. On each vertex we allow a total  maximal occupancy $\nu\in \mathbb{N}$. Then, the configuration space of the process on the graph $G$ is 

@@

\Omega_{x}:=\left\{n^x=(n_{1}^{x},\ldots,n_{N}^{x})\in\mathbb{N}_0^{N}\;:\; \sum_{a=1}^{N}n_{a}^{x}=\twoj\right\}\,.

@@

where  $ \omega_{x,y}\geq 0$ are so-called conductances and $\Gamma_{x}\geq 0$ local inhomogeneities. The generator $\mathcal{L}_{x,y}$ is called the \textit{edge generator}, while $\mathcal{L}_{x}$ is called the \textit{site generator}. These linear operators act on functions $f:\Omega\to \mathbb{R}$ as follows

@@

\end{cases}\,.
This means that on the edge $(x,y)\in \mathcal{E}$  a particle of type $a$ at site $x$ is exchanged with a particle of type $b$ at site $y$ at rate $\omega_{x,y}n_{a}^{x}n_{b}^{y}$. Furthermore, on each site $x\in V$  a particle of type $b$ is replaced with a particle of type $a$ at rate $\Gamma_{x}\alpha_{a}^{x}n_{b}^{x}$. For the sake of notation we denote $|\alpha^{x}|=\sum_{a=1}^{N}\alpha_{a}^{x}$. 
See Figure \ref{fig:1} and  Figure \ref{fig:2} for a visualisation of the dyamics. 

@@

\alpha_{a}^{x}=\alpha_{a}\qquad \forall x\in V\,.

@@

{\color{red}add/improve explanaition of entire subsection}
\subsection{The Lie algebraic description}

Consider the Lie algebra $gl(N)$ with generators denoted by $\EE_{ab}$ with $a,b\in \{1,\ldots,N\}$ and commutation relations
\begin{equation}\label{eq:comgl}
\left[\EE_{ab},\EE_{cd}\right]=\EE_{ad}\delta_{cb}-\EE_{cb}\delta_{ad}\qquad \forall a,b\in \{1,\ldots,N\}\,.
\end{equation}
The finite-dimensional representations are labelled by partitions $\lambda=(\lambda_1,\lambda_2,\ldots,\lambda_N)$ of $\nu$ with $\lambda_i\in \mathbb{N}$, $\lambda_i\geq \lambda_{i+1}$ and $\sum_{i=1}^N \lambda_i = \nu$.  
We are interested in the {\em symmetric} finite-dimensional representations with 
\begin{equation}\label{eq:dynkin}
    \lambda=(\twoj,0,\ldots,0) \qquad\text{where}\qquad \twoj\in\mathbb{N}\,.
\end{equation} 
The dimension $M_\twoj$ of this symmetric representations is given by the combination of $N$ objects in $\twoj$ positions with repetition, namely
\begin{equation}
	M_\twoj= \frac{(N+\twoj-1)!}{\twoj  !(N-1)!}
\end{equation} 
The basis elements of the vector space $\mathbb{C}^{M_\twoj}$ are the column vectors denoted by
\begin{equation}
  |n\rangle=  |n_{1},\ldots,n_{N}\rangle,\quad \text{with}\quad n_{i}\in\mathbb{N}_{0}\quad \text{sucht that}\quad \sum_{i=1}^{N}n_{i}=\nu\,.
\end{equation}
%where $\sum_{a=1}^{N}n_{i}=\nu$. 
The basis vectors satisfy the orthogonality relation with respect to the Euclidean scalar product 
\begin{equation}\label{ortho}
   \langle m|n \rangle =\langle m_{1},\ldots,m_{N}|n_{1},\ldots,n_{N}\rangle=\prod_{a=1}^{N}\delta_{\xi_{a},n_{a}}
\end{equation}
where  $ \langle m_{1},\ldots,m_{N}|$ is the row vector obtained by transposing $|m_{1},\ldots,m_{N}\rangle$ and $\delta_{\xi_{a},n_{a}}$ is the Kronecker delta. 
The explicit action of the algebra generators on the basis  vectors $|n\rangle$ is the following:
\begin{equation}\label{actionE}
	\begin{cases}
		E_{ab}|n_{1},\ldots,n_{a},\ldots,n_{b},\ldots,n_{N}\rangle =n_{b}|n_{1},\ldots,n_{a}+1,\ldots,n_{b}-1,\ldots,n_{N}\rangle\quad a\neq b\\[0.1cm]
		E_{aa}|n_{1},\ldots,n_{a},\ldots,n_{N}\rangle = n_{a} |n_{1},\ldots,n_{a},\ldots,n_{N}\rangle
	\end{cases}\,.
\end{equation}  
The matrices defined in this way satisfy the commutation relations \eqref{eq:comgl} and yield Dynkin weight \eqref{eq:dynkin}. \\
{\color{red} Is this remark relevant for us?}
\newline 
\textbf{Remark}: it is possible to define these matrices in terms of creation and annihilation operators: see Appendix \ref{appA}.
\\ \\
\textbf{Remark}: The symmetric representations $\lambda=(\twoj,0,\ldots,0)$ are dual to the representations $\lambda=(\twoj,\ldots,\twoj,0)$ that can be obtained via 
\begin{equation}
   \bar E_{ab}=\nu\delta_{ab}-E_{N-b+1,N-a+1}
\end{equation}
{\color{red} This needs to be checked and give alternative form of Hamiltonian?}\\
By the Lie algebra above we describe the process with generator \eqref{Generator}. The state space \eqref{stateSpace} is the vector space with basis elements

@@

\subsection{Integrable process on a line segment}
{\color{red}Introduce integrable model here}
